Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-10-28 manuscript.tex
agregue algunas referencias de las notas de mendeley

@@

HACER DISCUSION FUERTE DE ESTOS PAPERS: \cite{balbi_impact_2018,cirkovic_temporal_2004,grimaldi_signal_2017,smith_broadcasting_2009}

>>>>

\citet{bloetscher_using_2019} uses a probabilistic approach, though
still strongly motivated by the Drake equation, to obtain a
propbabilistic measure for the number of civilizations in the Galaxy.
To that end, perform MonteCarlo Markov Chains over each factor of the
Drake equation, and combine the means to obtain a probabilistic
result. It is worth mentioning that the author proposes a lof-normal
target distribution to compute the posterior probabilities. This
approach, which assigns probability distributions to the Drake
factors. This study concludes that there is a very low probability for
Earth to make contact with another extraterrestrail civilization.

\citet{smith_broadcasting_2009} uses a analytical model to compute the
probabilities of contact between two randomly located civilizations,
and the waiting time for the first contact, assuming a fixed maximum
broadcasting distance.

\citet{balbi_impact_2018} investigate the chance of communicating
civilizations making causal contact within a volume surrounding the
location of the Earth, using a statistical model to compute the
occurrence of causal contacts. The author stresses the fact that the
causal contact requirement involves the distance between
civilizations, their lifespan and their times of appeareance.  This is
important since the time it takes the light to travel across the
Galaxy is much lesser than the lifetime of the Galaxy.

\citet{balbi_impact_2018} fix the total number of civilizations and
explore the parameter space that comprise three parameters, namely,
the distance to the Earth, the time of appeareance and the lifespan of
the communicating civilization. Each of these three variables are
drawn from a random distribution. The distribution of the distances
results from a uniform distribution of civilization within the plane
of the Galaxy. For the distribution of the characteristic time of
appeareance, the author explores and exponential and a trucated
Gaussian distributions. For the distribution of the lifespans, the
author choses an exponential distribution. The radius of influence is
set to 1000 ly.

\citet{balbi_impact_2018} finds that the fraction of communicating
civilizations vary with the choice of the statistical distribution for
the time of appeareance. For all analyzed distributions, the fraction
corresponding to a mean lifetime of 10$^9$ years and for a maximu
radius for the detection of the signal of 1000 ys, is roughly 0.1.

\citet{vukotic_astrobiological_2012} propose a simulation approach
based on probabilistic cellular automata (PCA) modeling. In this
framework, a complex system is modeled by a lattice of cells which
evolve at discrete time steps, acording to transition rules that take
into account for each cell the states of its neighbour cells.

The authors implement a PCA model to a network of cells which
represent life complexity on a 2-dimensional annular ring resembling
the GHZ. The authors set the GHZ between a minimum radius of 6 kpc and
a maximum radius of 10 kpc. Within this framework, the authors also
make several MonteCarlo simulations and analyze ensemble-averaged
results.

This work aims at analyzing the evolution of life, although it does
not account for the network of causal contacts among technological
civilizations.

%- - - -

@@

% HACER DISCUSION FUERTE DE ESTOS PAPERS: \cite{balbi_impact_2018,cirkovic_temporal_2004,grimaldi_signal_2017,smith_broadcasting_2009}
